An example exploratory analysis script

### 2024-06-27 code/eda-code/eda.qmd
I think this was just minor updates to eda file. I'm only just noticing i'm behind a commit/push.

```{r}
d1 %>% 
  mutate(years = year(Occurred.Date),
         years = as.character(years)
         ) %>% 
  filter(years == '2023' | years == '2022') %>% 
  group_by(Family.Violence, Zip.Code, years) %>% 
  summarize(cnt = n(), .groups = 'drop') %>% 
  group_by(Zip.Code, years) %>% 
  mutate(tot = sum(cnt)) %>% 
  relocate(tot, .after = years) %>% 
  mutate(Zip.Code = as.character(Zip.Code)) %>%
  as.data.frame() %>% 
  arrange(desc(tot)) %>% head(100) %>% 
  ggplot(aes(fill=Family.Violence, x= reorder(Zip.Code,cnt), y=cnt)) +
  geom_bar(position = 'stack', stat='identity') +
  facet_wrap(~years) +
  coord_flip()
```

>>>>

```{r}
d1 %>% 
  mutate(years = year(Occurred.Date),
         years = as.character(years)
         ) %>% 
  filter(years == '2003' | years == '2022') %>% 
  group_by(Family.Violence, Zip.Code, years) %>% 
  summarize(cnt = n(), .groups = 'drop') %>% 
  group_by(Zip.Code, years) %>% 
  mutate(tot = sum(cnt)) %>% 
  relocate(tot, .after = years) %>% 
  mutate(Zip.Code = as.character(Zip.Code)) %>%
  as.data.frame() %>% 
  arrange(desc(tot)) %>% head(100) %>% 
  ggplot(aes(fill=Family.Violence, x= reorder(Zip.Code,cnt), y=cnt)) +
  geom_bar(position = 'stack', stat='identity') +
  facet_wrap(~years) +
  coord_flip()
```
